Diffusion-limited mixing by incompressible flows

### 2017-10-04 nonlinearity/manuscript.tex
finished charlies revisions to abstract

\begin{abstract}
Incompressible flows can be effective mixers by appropriately advecting a passive tracer to produce small filamentation length scales. The Batchelor length scale \cite{Batchelor1959a} was proposed as thelower limit of length scales achievable in turbulent flows. Here, we provide numerical evidence that this limitation may be even more general, applying as well to all incompressible flows under mild physical constraints such as bounded enstrophy or energy. We consider local-in-time flow optimization under these flow intensity constraints with the objective of maximizing mixing rate performance. For enstrophy-bounded optimal flows, we find that the strength of diffusion has no impact on the long-term mixing rate performance. For energy-constrained optimal flows, we find that an increase in the strength of diffusion worsens this performance. We provide analytical lower bounds on mixing rates and length scales achievable under related constraints (pointwise bounded speed and rate-of-strain) by extending the work of \cite{JFM2011} and \cite{Chi-Cheu1996}.

>>>>

\begin{abstract}
Incompressible flows can be effective mixers by appropriately advecting a passive tracer to produce small filamentation length scales. The Batchelor length scale \cite{Batchelor1959a} was proposed as the lower limit of length scales achievable in turbulent flows. Here, we provide numerical evidence that this limitation may be even more general, applying as well to all incompressible flows under mild physical constraints such as bounded enstrophy or energy. We consider local-in-time flow optimization under these flow intensity constraints with the objective of maximizing mixing rate performance. We observe that, for enstrophy-bounded optimal flows, the strength of diffusion has no impact on the long-term mixing rate performance. For energy-constrained optimal flows, however an increase in the strength of diffusion decreases the mixing rate. We provide analytical lower bounds on mixing rates and length scales achievable under related constraints (pointwise bounded speed and rate-of-strain) by extending the work of \cite{JFM2011} and \cite{Chi-Cheu1996}.
